\chapter{Release notes}\index{release notes}
The tags, e.g. \jira{49}, are links to the \crava project management
system called
\href{http://www.atlassian.com/software/jira/}{JIRA}.
\index{JIRA, project management} Note that access permission is
required to be able to open the links.

\section{Changes from \crava Version 1.0 to Version 1.1}

\begin{description}

\item [New features:] \mbox{ }
  \begin{itemize}
    \item Allow background model to be specified with AI and\!/\!or
      \vp/\vs, as a complement to \vp, \vs, and $\rho$. Specify files
      for these parameters with keyword \kw{ai-file} and
      \kw{vp-vs-ratio-file}. \jira{214}
    \item Allow users to specify \vp/\vs for use in the
      reflection matrix.  Use keyword \kw{vp-vs-ratio}. \jira{219}
    \item Remove certain QC checks when \crava is run from
      \rms, as \rms will perform these tests. Activated with keyword
      \kw{rms-panel-mode}. \jira{221}
    \item When seismic data is given in SegY format, write the IL-XL
      range of data to the log file. \jira{230}, \jira{267}
    \item Create synthetic residuals which add up to original seismic
      when added to synthetic seismic. Activated with
      \kw{synthetic-residuals}. \jira{234}
    \item If the \kw{rms-panel-mode} mode has been requested and
      facies probabilities are not requested, well logs will not be
      (multi-parameter) filtered. \jira{242}
    \item Allow \vp/\vs to be estimated from wells. Activated
      with keyword \kw{vp-vs-ratio-from-wells}. If
      \kw{wavelet-estimation-interval} has been specified, this
      interval will also be used for the \vp/\vs estimate. \jira{247}
    \item If automatic SegY format detection fails, list trace
      header locations of known formats as well as their associated
      \crava-names. \jira{259}
    \item Give a warning if prior or posterior parameter correlations
      exceed one. To avoid this situation completely, some recoding is
      required. This is left for a later release (see
      \jira{257}). \jira{261}
    \item When specifying an area as UTM coordinates or surface,
      choose as inversion area the smallest IL-XL box that
      encloses the specified area. Activated with keyword
      \kw{snap-to-seismic-data}. \jira{266}
    \item Allow (some) traces to have bogus IL-XL information in
      header. If encountered, the IL-XL values are set to
      undefined. \jira{269}
    \item Write IL-XL values for well start positions whenever
      possible. This makes it easy to do inversion around a given
      well. \jira{270}
 \end{itemize}

\item [Changes:] \mbox{ }
  \begin{itemize}
    \item When the prior correlation between \vp and \vs cannot be
      estimated from well data it is set to $1/\sqrt{2}\approx
      0.7$. \jira{220}
    \item Made blocking of facies deterministic. If a cell has the
      same facies count for $n$ different facies, the cell value
      becomes facies\_to\_choose $= (k + 1)\ \%\ n$, where $k$ is the
      layer number. This used to be randomly chosen, so that identical
      runs could give different facies predictions. \jira{249}
    \item Changed the computation of SegY geometry, and improved error messages. The new version should be more accurate and robust.
  \end{itemize}

\item [Bug fixes:] \mbox{ }
  \begin{itemize}
    \item Fixed crash in background modelling when there were
      (unrealistically) few layers in grid. \jira{200}
    \item Background volumes of AI and\!/\!or \vp/\vs containing undefined
      values caused troubles. The fix is to set such undefined values
      to global mean. \jira{222}
    \item Removed bugs in estimation of wavelet norm, which indirectly
      led to ringing in inversion results. \jira{223}
    \item Number of allocated grids were incorrectly counted when
      estimating total memory requirement for \crava. \jira{251}
    \item Fixed crash when interval was specified with option
      \kw{interval-one-surface}. Wavelets had not been transformed
      prior to constant thickness inversion. Also, a wavelet polarity
      bug was fixed. New test cases 16 and 17 were added to avoid
      future constant thickness and wavelet polarity related
      bugs. \jira{252}, \jira{253}
    \item For short wells, deviation angles were incorrectly estimated
      due to an 10ms sample requirement. Also, the angle was
      calculated between well start and well end instead of for
      trajectory tangents.
    \item Fixed crash when project directory could not be
      created. This was a bug in the throw/catch system of
      NRLib. \jira{256}
    \item Fixed several bugs encountered when using 3D prior facies
      probability volumes. \jira{272}
    \item Fixed bug with interpolation of Storm-grids used for input.
 \end{itemize}
\end{description}
