
\chapter{CRAVA model file reference manual}\index{reference manual, CRAVA model file elements}
\label{ap:model-file-reference}
\index{CRAVA model file@Crava model file!reference manual for elements}
The numbering shows the command grouping. A command with no subnumbering expects a value to be given, otherwise, it is only a grouping of other commands.

File names are currently given with a path relative to the directory settings in <project-settings>-<io-settings>-<input/output/top-directory>. If these are not given, the path will always be relative to the working directory.

All commands are optional, unless otherwise stated. A necessary command under an optional is only necessary if the optional is given.


\section{\hbracket{actions}\necessary} \newkw{actions}
 \slist
   \item \Description Controls the main purpose of the run.
   \item \Argument Elements specifying the main purpose
   \item \Default
 \elist

\subsection{\hbracket{mode}\necessary}  \newkw{mode}
 \slist
   \item \Description Inversion: Invert seismic input data to elastic parameters and/or facies probabilities. Needs seismic data and volume, all other missing data will be estimated.
Forward: Create seismic response from background model. Not able to estimate anything.
Estimation: Checks input data and performs estimation of lacking information for inversion, but stops before inversion.
   \item \Argument 'inversion', 'forward' or 'estimation'
   \item \Default
 \elist

\subsection{\hbracket{inversion-settings}}  \newkw{inversion-settings}
 \slist
   \item \Description Controls aspects of the inversion. Only valid with the \kw{mode} 'inversion' above.
   \item \Argument Elements controlling the inversion
   \item \Default
 \elist

\subsubsection{\hbracket{prediction}}  \newkw{prediction}
 \slist
   \item \Description Controls whether predicted elastic parameters will be generated.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{simulation}}  \newkw{simulation}
 \slist
   \item \Description Controls aspects of the simulation of elastic parameters.
   \item \Argument Elements controlling the simulation of elastic parameters
   \item \Default
 \elist



\paragraph{\hbracket{seed}}  \newkw{seed}
 \slist
   \item \Description A number used to initialize the random generator. Running a model file with a given seed will give the same simulation results each time.
   \item \Argument Integer
   \item \Default 0.0
 \elist

\paragraph{\hbracket{seed-file}}  \newkw{seed-file}
 \slist
   \item \Description Alternative to \kw{seed}. This is an ASCII file containing a number. At the termination of the run, the file will be overwritten with a seed generated by the random generator. Thus, a model file using this will generate different simulation results on sequential runs.
   \item \Argument ASCII file containing a number
   \item \Default
 \elist

\paragraph{\hbracket{number-of-simulations}}  \newkw{number-of-simulations}
 \slist
   \item \Description Integer value giving the number of stochastic realizations to generate.
   \item \Argument Integer
   \item \Default 0
 \elist

\subsubsection{\hbracket{condition-to-wells}}  \newkw{condition-to-wells}
 \slist
   \item \Description Should the realizations be kriged to well data?
   \item \Argument 'yes' or 'no'
   \item \Default 'yes' if not the \kw{simulation} command is used.
 \elist

\subsubsection{\hbracket{facies-probabilities}}  \newkw{facies-probabilities}
 \slist
   \item \Description Triggers generation of facies probabilities. Absolute: facies probabilities are generated based on inverted parameters including background model. Relative: Background model is not used when facies probabilities are generated.
   \item \Argument 'absolute' or 'relative'
   \item \Default
 \elist

\subsubsection{\hbracket{synthetic-seismic}}  \newkw{synthetic-seismic}
 \slist
   \item \Description Should we generate synthetic seismic from the inverted data?
   \item \Argument 'yes' or 'no'
   \item \Default 
 \elist



\subsection{\hbracket{estimation-settings}} \newkw{estimation-settings}
 \slist
   \item \Description Controls what will be estimated. Only valid with the \kw{mode} 'estimation'. Note that these commands can only turn off estimations - a parameter that is given will not be estimated even if it says so here.
   \item \Argument Elements controlling what to estimate
   \item \Default
 \elist

\subsubsection{\hbracket{estimate-background}}  \newkw{estimate-background}
 \slist
   \item \Description If 'no', background will not be estimated unless needed for other estimation.
   \item \Argument 'yes' or 'no'
   \item \Default 'yes'
 \elist

\subsubsection{\hbracket{estimate-correlations}}  \newkw{estimate-correlations}
 \slist
   \item \Description If 'no', correlations will not be estimated unless needed for other estimation.
   \item \Argument 'yes' or 'no'
   \item \Default 'yes'
 \elist

\subsubsection{\hbracket{estimate-wavelet-or-noise}}  \newkw{estimate-wavelet-or-noise}
 \slist
   \item \Description If 'no', wavelets and/or noise will not be estimated unless needed for other estimation.
   \item \Argument 'yes' or 'no'
   \item \Default 'yes'
 \elist

 \section{\hbracket{project-settings}\necessary} \newkw{project-settings}
 \slist
   \item \Description Controls inversion volume, output and advanced program settings.
   \item \Argument Elements controlling inversion volume, output and advanced program settings
   \item \Default
 \elist

\subsection{\hbracket{output-volume}\necessary} \newkw{output-volume}
 \slist
   \item \Description Defines the core inversion volume. All grid output will be given in this volume.
   \item \Argument Elements defining the core inversion volume.
   \item \Default
 \elist

\subsubsection{\hbracket{interval-two-surfaces}} \newkw{interval-two-surfaces}
 \slist
   \item \Description One way to give the top and bottom limitations. Must be used if output in depth domain is desired. This or \kw{interval-one-surface} must be given.
   \item \Argument
   \item \Default
 \elist

\paragraph{\hbracket{top-surface}\necessary} \newkw{top-surface}
 \slist
   \item \Description File name(s) for top surface file(s).
   \item \Argument Elements controlling the top surface
   \item \Default
 \elist

\subparagraph{\hbracket{time-file}} \newkw{time-file}
 \slist
   \item \Description File name for storm grid file giving top surface in time. This or \kw{time-value} must be given.
   \item \Argument File name
   \item \Default
 \elist

\subparagraph{\hbracket{time-value}} \newkw{time-value}
 \slist
   \item \Description Value giving the top time for the inversion interval. This or \kw{time-file} must be given.
   \item \Argument Value
   \item \Default
 \elist

 \subparagraph{\hbracket{depth-file}} \newkw{depth-file}
 \slist
   \item \Description File name for storm grid file giving top surface in depth.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{base-surface}\necessary} \newkw{base-surface}
 \slist
   \item \Description File name(s) for base surface file(s).
   \item \Argument Elements controlling the base surface
   \item \Default
 \elist

\subparagraph{\hbracket{time-file}} \rnewkw{time-file}{time-file2}
\slist
   \item \Description File name for storm grid file giving base surface in time. This or \rkw{time-value}{time-value2} must be given.
   \item \Argument File name
   \item \Default
\elist

\subparagraph{\hbracket{time-value}} \rnewkw{time-value}{time-value2}
\slist
   \item \Description Value giving the base time for the inversion interval. This or \rkw{time-file}{time-file2} must be given.
   \item \Argument Value
   \item \Default
\elist

\subparagraph{\hbracket{depth-file}} \rnewkw{depth-file}{depth-file2}
\slist
   \item \Description File name for storm grid file giving base surface in depth.
   \item \Argument File name
   \item \Default
\elist


\paragraph{\hbracket{number-of-layers}} \newkw{number-of-layers}
 \slist
   \item \Description Integer value giving how many layers to use between top and base surface.
   \item \Argument Integer
   \item \Default
 \elist

\paragraph{\hbracket{velocity-field}} \newkw{velocity-field}
 \slist
   \item \Description File name for storm grid file. Gives more detailed depth conversion information. Without this, constant velocity per trace is used. If only one depth surface is given, this is used to compute the other. Otherwise, the depth interval will always match both surfaces, but the velocity field is scaled and used for internal depth computations. Can not be used with \kw{velocity-field-from-inversion}.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{velocity-field-from-inversion}} \newkw{velocity-field-from-inversion}
 \slist
   \item \Description If given, velocity field from inversion is used for depth conversion. See \kw{velocity-field} for details on how this is done. Can not be used with \kw{velocity-field}.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{interval-one-surface}} \newkw{interval-one-surface}
 \slist
   \item \Description Using this command gives parallel top and base of inversion interval. This or \kw{interval-two-surfaces} must be given.
   \item \Argument Elements for parallel top and base inversion interval
   \item \Default
 \elist

\paragraph{\hbracket{reference-surface}} \newkw{reference-surface}
 \slist
   \item \Description File name for storm surface file. The top and base surfaces for the inversion interval will be parallel to this.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{shift-to-interval-top}} \newkw{shift-to-interval-top}
 \slist
   \item \Description Value giving the distance from reference surface to top surface. This value is added to the reference surface to create the top surface.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{thickness}}\newkw{thickness}
 \slist
   \item \Description Value giving the thickness of the inversion interval. This value is added to the top surface to create the base surface.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{sample-density}}\newkw{sample-density}
 \slist
   \item \Description Value giving the thickness of a layer in the inversion interval. The thickness should be divisible by this value.
   \item \Argument Value
   \item \Default
 \elist

\subsubsection{\hbracket{area}}\newkw{area}
 \slist
   \item \Description This command holds the parameters defining the lateral extent of the inversion volume. If this command is not given, the information is taken from the first seismic data file, or from Vp if we do forward modeling(mode set to forward).
   \item \Argument Elements defining lateral extent of inversion volume
   \item \Default
 \elist

\paragraph{\hbracket{reference-point-x}}\newkw{reference-point-x}
 \slist
   \item \Description Value giving the x-coordinate of a corner of the area.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{reference-point-y}}\newkw{reference-point-y}
 \slist
   \item \Description Value giving the y-coordinate of a corner of the area.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{length-x}}\newkw{length-x}
 \slist
   \item \Description Value giving the area length along the rotated x-axis.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{length-y}}\newkw{length-y}
 \slist
   \item \Description Value giving the area length along the rotated y-axis.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{sample-density-x}}\newkw{sample-density-x}
 \slist
   \item \Description Cell size along the rotated x-axis.
   \item \Argument Integer
   \item \Default
 \elist

\paragraph{\hbracket{sample-density-y}}\newkw{sample-density-y}
 \slist
   \item \Description Cell size along the rotated y-axis.
   \item \Argument Integer
   \item \Default
 \elist

\paragraph{\hbracket{angle}}\newkw{angle}
 \slist
   \item \Description Orientation of the azimuth.
   \item \Argument
   \item \Default
 \elist

\subsection{\hbracket{time-3D-mapping}} \newkw{time-3D-mapping}
 \slist
   \item \Description Defines the mapping between pseudo depth and local time in the target area for 3D wavelet.
   \item \Argument Reference depth, velocity and time surface for mapping
   \item \Default
 \elist

\subsubsection{\hbracket{reference-depth}} \newkw{reference-depth}
 \slist
   \item \Description Holds the z-value for the reference depth for target area
   \item \Argument Depth in meter
   \item \Default
\elist

\subsubsection{\hbracket{average-velocity}} \newkw{average-velocity}
 \slist
   \item \Description Holds the average velocity in the target area
   \item \Argument Velocity in meter/second
   \item \Default
\elist

\subsubsection{\hbracket{reference-time-surface}} \newkw{reference-time-surface}
 \slist
   \item \Description Filename for the time surface corresponding to the reference depth. 
   \item \Argument File name
   \item \Default
\elist

\subsection{\hbracket{io-settings}} \newkw{io-settings}
 \slist
   \item \Description Holds commands that deal with what output to give and where, and where to find input.
   \item \Argument Elements controlling output and input
   \item \Default
 \elist

\subsubsection{\hbracket{top-directory}} \newkw{top-directory}
 \slist
   \item \Description Directory name giving the working directory for the model file. Must end with directory separator.
   \item \Argument Directory name
   \item \Default
 \elist

\subsubsection{\hbracket{input-directory}} \newkw{input-directory}
 \slist
   \item \Description Directory name, relative to \kw{top-directory}, for root directory for input files. Must end with directory separator.
   \item \Argument Directory name
   \item \Default
 \elist

\subsubsection{\hbracket{output-directory}} \newkw{output-directory}
 \slist
   \item \Description Directory name, relative to \kw{top-directory}, for root directory for output files. Must end with directory separator.
   \item \Argument Directory name
   \item \Default
 \elist

\subsubsection{\hbracket{output-types}}\newkw{output-types}
 \slist
   \item \Description All commands directly controlling actual result output are gathered here.
   \item \Argument Elements controlling result output
   \item \Default
 \elist

\paragraph{\hbracket{grid-output}}\newkw{grid-output}
 \slist
   \item \Description All commands related to output given as grids are gathered here.
   \item \Argument Elements controlling output given as grids
   \item \Default
 \elist

\subparagraph{\hbracket{domain}}\newkw{domain}
 \slist
   \item \Description Commands specifying which domain output should be in.
   \item \Argument Elements controlling the output domain
   \item \Default
 \elist

\subsubparagraph{\hbracket{depth}}\newkw{depth}
 \slist
   \item \Description Should output come in depth domain? Requires information under \kw{interval-two-surfaces}.
   \item \Argument 'yes' or 'no'
   \item \Default 'no'
 \elist

\subsubparagraph{\hbracket{time}}\newkw{time}
 \slist
   \item \Description Should output come in time domain?
   \item \Argument 'yes' or 'no'
   \item \Default 'yes'
 \elist

\subparagraph{\hbracket{format}}\newkw{format}
 \slist
   \item \Description Control of the format of output grids.
   \item \Argument Elements controlling the format of output grids
   \item \Default
 \elist

\subsubparagraph{\hbracket{segy}}\newkw{segy}
 \slist
   \item \Description Should grid output come as segy?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{storm}}\newkw{storm}
 \slist
   \item \Description Should grid output come as storm?
   \item \Argument 'yes' or 'no'
   \item \Default 'yes' if \kw{format} command is not given.
 \elist


\subsubparagraph{\hbracket{crava}}\newkw{crava}
 \slist
   \item \Description Should grid output come in crava binary format?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{sgri}}\newkw{sgri}
 \slist
   \item \Description Should grid output come as storm sgri?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{ascii}}\newkw{ascii}
 \slist
   \item \Description Should grid output come as storm ascii?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{parameters}}\newkw{parameters}
 \slist
   \item \Description Controls which grid parameters to output. All are 'yes' or 'no'.
   \item \Argument Elements controlling which grid parameters to output
   \item \Default If this command is not given, vp, vs and density are written.
 \elist

\subsubparagraph{\hbracket{vp}}\newkw{vp}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{vs}}\newkw{vs}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{density}}\newkw{density}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{lame-lambda}}\newkw{lame-lambda}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist


\subsubparagraph{\hbracket{lame-mu}}\newkw{lame-mu}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{poisson-ratio}}\newkw{poisson-ratio}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{ai}}\newkw{ai}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{si}}\newkw{si}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{vp-vs-ratio}}\newkw{vp-vs-ratio}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{murho}}\newkw{murho}
\slist
  \item \Description
  \item \Argument 'yes' or 'no'
  \item \Default
\elist

\subsubparagraph{\hbracket{lambdarho}}\newkw{lambdarho}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
\elist

\subsubparagraph{\hbracket{correlations}}\newkw{correlations}
 \slist
   \item \Description These are the posterior correlations between vp, vs and density after inversion.
   \item \Argument 'yes' or 'no'
   \item \Default
\elist

\subsubparagraph{\hbracket{residuals}}\newkw{residuals}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
\elist

\subsubparagraph{\hbracket{background}}\newkw{background}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
\elist

\subsubparagraph{\hbracket{background-trend}}\newkw{background-trend}
 \slist
   \item \Description
   \item \Argument 'yes' or 'no'
   \item \Default
\elist

\subsubparagraph{\hbracket{seismic-data}}\newkw{seismic-data}
 \slist
   \item \Description Write original seismic data to file.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{time-to-depth-velocity}}\newkw{time-to-depth-velocity}
 \slist
   \item \Description Write time-to-depth velocity to file.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubparagraph{\hbracket{extra-grids}}\newkw{extra-grids}
 \slist
   \item \Description Temporary, will be replaced. Currently triggers writing of
   \begin{itemize}
   \item Estimated background files in extended versions (go above and below inversion volume).
   \item Estimated background files in standard volume.
   \end{itemize}
   \item \Argument 'yes' or 'no'
   \item \Default
\elist


\paragraph{\hbracket{well-output}}\newkw{well-output}
 \slist
   \item \Description Collects all output that can be given in well format. Wells contain logs for vp, vs and density, each of these in four versions: Raw, filtered to background frequency, filtered to seismic frequency and seismic resolution. In addition, the facies log is written if found.
   \item \Argument Elements collecting output given in well format
   \item \Default
 \elist

\subparagraph{\hbracket{format}}\rnewkw{format}{format2}
 \slist
   \item \Description Controls well formats used for output. Default is RMS.
   \item \Argument Elements controlling the formats used for output
   \item \Default
 \elist

\subsubparagraph{\hbracket{rms}}\newkw{rms}
 \slist
   \item \Description Controls if wells are written on RMS format.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

 \subsubparagraph{\hbracket{norsar}}\newkw{norsar}
 \slist
   \item \Description Controls if wells are written on NORSAR format.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{wells}}\newkw{wells}
 \slist
   \item \Description Writes wells following original sampling density.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{blocked-wells}}\newkw{blocked-wells}
 \slist
   \item \Description Writes wells sampled to internal grid resolution.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{blocked-logs}}\newkw{blocked-logs}
 \slist
   \item \Description Not currently active.
   \item \Argument
   \item \Default
 \elist

\paragraph{\hbracket{other-output}}\newkw{other-output}
 \slist
   \item \Description Controls output that is neither standard grid nor well.
   \item \Argument Elements controlling output
   \item \Default
 \elist

\subparagraph{\hbracket{wavelets}}\newkw{wavelets}
 \slist
   \item \Description Write wavelet to file. Mainly for use with wavelet estimation.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{extra-surfaces}}\newkw{extra-surfaces}
 \slist
   \item \Description Temporary, will be replaced. Currently writes:
   \begin{itemize}
   \item Top and base surface for constant thickness interval used for log filtering and facies probabilities.
   \item Top and base surface for extended inversion interval computed from correlation surface.
   \item Top and base surface for background estimation interval (larger than inversion interval).
   \item Estimated local wavelet shift.
   \item Estimated local wavelet scale.
   \end{itemize}
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{prior-correlations}}\newkw{prior-correlations}
 \slist
   \item \Description Write prior correlation files.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{background-trend-1d}}\newkw{background-trend-1d}
 \slist
   \item \Description Write the background trend as 1D curve.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{file-output-prefix}}\newkw{file-output-prefix}
 \slist
   \item \Description Common prefix added to all files written in the run. Identifies the run.
   \item \Argument String
   \item \Default
 \elist

\subsubsection{\hbracket{log-level}}\newkw{log-level}
 \slist
   \item \Description Not very useful, as very little additional output is given.
   \item \Argument Integer
   \item \Default Default is 1, may be increased to get more details.
 \elist

\subsection{\hbracket{advanced-settings}} \newkw{advanced-settings}
 \slist
   \item \Description A collection of different commands that control advanced aspects of the program control.
   \item \Argument Commands controlling advanced aspects of the program control
   \item \Default
 \elist

\subsubsection{\hbracket{fft-grid-padding}}\newkw{fft-grid-padding}
 \slist
   \item \Description Controls the padding size, can be used to optimize memory or improve visual results. Padding should be at least one range laterally, and a wavelet length vertically to avoid edge effects.
   \item \Argument Elements controlling the padding size
   \item \Default
 \elist

\paragraph{\hbracket{x-fraction}}\newkw{x-fraction}
 \slist
   \item \Description Value telling how large the padding in the x-direction should be relative to the x-length. %If the padding command is not called, proper padding will be estimated.
   \item \Argument Value
   \item \Default 0.0
 \elist

\paragraph{\hbracket{y-fraction}}\newkw{y-fraction}
 \slist
   \item \Description Value telling how large the padding in the x-direction should be relative to the y-length.
   \item \Argument Value
   \item \Default 0.0
 \elist

\paragraph{\hbracket{z-fraction}}\newkw{z-fraction}
 \slist
   \item \Description Value telling how large the padding in the x-direction should be relative to the thickness.
   \item \Argument Value
   \item \Default 0.0
 \elist

\subsubsection{\hbracket{use-intermediate-disk-storage}} \newkw{use-intermediate-disk-storage}
 \slist
   \item \Description When running under windows with less memory than the program requires, this activates a built-in smart swap that increases performance. Linux/unix swap is so efficient that this option has no effect there.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{maximum-relative-thickness-difference}}\newkw{maximum-relative-thickness-difference}
 \slist
   \item \Description Value giving the limit of how small the minimum interval thickness can be relative to maximum. If this gets too low, the transformation to stationarity for the FFT-algorithm gives strange results.
   \item \Argument Value
   \item \Default Default is 0.5, which is ok. Slightly smaller seems to work as well.
 \elist

\subsubsection{\hbracket{frequency-band}}\newkw{frequency-band}
 \slist
   \item \Description This command controls the frequency band of the inversion, so high and/or low frequencies can be filtered away. This ought to be done by the wavelet, but can be done here.
   \item \Argument Elements controlling the frequency band of the inversion
   \item \Default
 \elist

\paragraph{\hbracket{low-cut}}\newkw{low-cut}
 \slist
   \item \Description Value setting the minimum frequency affected by the inversion.
   \item \Argument Value
   \item \Default 5.0
 \elist

\paragraph{\hbracket{high-cut}}\newkw{high-cut}
 \slist
   \item \Description Value setting the maximum frequency affected by the inversion.
   \item \Argument Value
   \item \Default 55.0
 \elist

\subsubsection{\hbracket{energy-threshold}}\newkw{energy-threshold}
 \slist
   \item \Description If the energy in a trace falls below this threshold relative to the average, the trace is interpolated from neighbors.
   \item \Argument Value
   \item \Default 0.0
 \elist

\subsubsection{\hbracket{wavelet-tapering-length}}\newkw{wavelet-tapering-length}
 \slist
   \item \Description Value giving the length of the wavelet to be estimated in ms.
   \item \Argument Value
   \item \Default 200.0
 \elist

\subsubsection{\hbracket{minimum-relative-wavelet-amplitude}}\newkw{minimum-relative-wavelet-amplitude}
 \slist
   \item \Description Value giving the ratio between the smallest relevant amplitude and the largest amplitude of peaks on an estimated wavelet. Edge peaks below this ratio are removed.
   \item \Argument Value
   \item \Default 0.05
 \elist

\subsubsection{\hbracket{maximum-wavelet-shift}}\newkw{maximum-wavelet-shift}
 \slist
   \item \Description Value controlling how much the wavelet is allowed to be shifted when doing estimation of wavelet or noise.
   \item \Argument Value
   \item \Default 11.0
 \elist

 \subsubsection{\hbracket{white-noise-component}}\newkw{white-noise-component}
 \slist
   \item \Description In order to stabilize the inversion, we need to interpret some of the noise as white. This value controls the fraction.
   \item \Argument Value between 0 and 1.
   \item \Default 0.1
 \elist

\subsubsection{\hbracket{reflection-matrix}}\newkw{reflection-matrix}
\slist
   \item \Description The file should be a 3 by  number of seismic data cubes ascii matrix. The first column is the factor used for vp for each cube setting (angle and ps/pp) when computing the reflection coefficients. The second and third are for vs and density.
   \item \Argument File name
   \item \Default Linearized Aki-Richards.
 \elist

\subsubsection{\hbracket{kriging-data-limit}}\newkw{kriging-data-limit}
 \slist
   \item \Description Integer value giving the limit for the amount of well data used to krige each point. A high value gives a smoother and more exact field, but takes more time.
   \item \Argument Integer
   \item \Default 300
 \elist

\subsubsection{\hbracket{debug-level}}\newkw{debug-level}
 \slist
   \item \Description Gives debug messages and output. Not intended for use except on request by NR.
   \item \Argument Integer value 0, 1 or 2.
   \item \Default 0
 \elist

 \section{\hbracket{survey}\necessary} \newkw{survey}
 \slist
   \item \Description All information about the seismic data is collected here.
   \item \Argument Elements containing information about the seismic data
   \item \Default
 \elist

 \subsection{\hbracket{angular-correlation}}\newkw{angular-correlation}
 \slist
   \item \Description 1D variogram. Gives the noise correlation between survey angles.
   \item \Argument 1D variogram
   \item \Default
 \elist

 \subsection{\hbracket{segy-start-time}}\newkw{segy-start-time}
 \slist
   \item \Description Global start time for segy cubes. This is used if no individual time is given for a segy-cube.
   \item \Argument Value
   \item \Default
 \elist

\subsection{\hbracket{angle-gather}\necessary}\newkw{angle-gather}
 \slist
   \item \Description Repeatable command, one for each seismic data cube.
   \item \Argument Elements containing information about the different seismic data cubes
   \item \Default
 \elist

\subsubsection{\hbracket{offset-angle}\necessary}\newkw{offset-angle}
 \slist
   \item \Description This is the angle for the seismic data cube.
   \item \Argument Value
   \item \Default
 \elist

\subsubsection{\hbracket{seismic-data}\necessary}\newkw{seismic-data}
 \slist
   \item \Description Information about the seismic data cube.
   \item \Argument Elements containing information about the seismic data cube
   \item \Default
 \elist

\paragraph{\hbracket{file-name}\necessary}\newkw{file-name}
 \slist
   \item \Description File name for the seismic data cube. This can be
     a segy file, a storm binary file or a crava binary file. The file
     type will be automatically detected.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{start-time}}\newkw{start-time}
 \slist
   \item \Description Value giving the start time for this segy file.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{segy-format}}\newkw{segy-format}
 \slist
   \item \Description Information about the segy format. By default, CRAVA recognizes SeisWork and IESX.
   \item \Argument Elements containing information about the segy format
   \item \Default
 \elist

\subparagraph{\hbracket{standard-format}}\newkw{standard-format}
 \slist
   \item \Description Giving the starting format for modifications.
   \item \Argument 'seisworks' or 'iesx'
   \item \Default 'seisworks'
 \elist

\subparagraph{\hbracket{location-x}}\newkw{location-x}
 \slist
   \item \Description The byte location for the x-coordinate in the trace header.
   \item \Argument Integer
   \item \Default
 \elist

\subparagraph{\hbracket{location-y}}\newkw{location-y}
 \slist
   \item \Description The byte location for the y-coordinate in the trace header.
   \item \Argument Integer
   \item \Default
 \elist

\subparagraph{\hbracket{location-il}}\newkw{location-il}
 \slist
   \item \Description The byte location for the inline in the trace header.
   \item \Argument Integer
   \item \Default
 \elist

\subparagraph{\hbracket{location-xl}}\newkw{location-xl}
 \slist
   \item \Description The byte location for the crossline in the trace header.
   \item \Argument Integer
   \item \Default
 \elist

\subparagraph{\hbracket{bypass-coordinate-scaling}}\newkw{bypass-coordinate-scaling}
 \slist
   \item \Description Indicates whether coordinate scaling information should be used.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\paragraph{\hbracket{type}}\newkw{type}
 \slist
   \item \Description Indicating the type of seismic data. Note that if both pp and ps cubes are used, these must be aligned.
   \item \Argument 'pp' or 'ps'
   \item \Default 'pp'
 \elist

\subsubsection{\hbracket{wavelet}}\newkw{wavelet}
 \slist
   \item \Description Information about the wavelet for this angle and seismic type. If not given, the wavelet will be estimated.
   \item \Argument Elements containing information about the wavelet and seismic type
   \item \Default
 \elist

\paragraph{\hbracket{file-name}}\rnewkw{file-name}{file-name2}
 \slist
   \item \Description File name for wavelet file. If not given, wavelet is estimated.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{scale}}\newkw{scale}
 \slist
   \item \Description Wavelet read from file is multiplied by this. Has no meaning when wavelet is estimated.
   \item \Argument Value
   \item \Default
 \elist

\paragraph{\hbracket{estimate-scale}}\newkw{estimate-scale}
 \slist
   \item \Description Should global scale be estimated?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\paragraph{\hbracket{local-wavelet}}\newkw{local-wavelet}
 \slist
   \item \Description The amplitude and shift of the wavelet may be modified locally by 2D fields for shift and scale values. This is handled here.
   \item \Argument Elements modifying the amplitude and shift of the wavelet
   \item \Default
 \elist

\subparagraph{\hbracket{shift-file}}\newkw{shift-file}
 \slist
   \item \Description File name for storm surface file giving the local shift for the wavelet. Not allowed when wavelet is estimated.
   \item \Argument File name
   \item \Default
 \elist

\subparagraph{\hbracket{scale-file}}\newkw{scale-file}
 \slist
   \item \Description File name for storm surface file giving local scale for the wavelet. Not allowed when wavelet is estimated.
   \item \Argument File name
   \item \Default
 \elist

\subparagraph{\hbracket{estimate-shift}}\newkw{estimate-shift}
 \slist
   \item \Description Should a local shift be estimated? Not allowed with \kw{shift-file}, but can be used both with given and estimated wavelet.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subparagraph{\hbracket{estimate-scale}}\rnewkw{estimate-scale}{estimate-scale2}
 \slist
   \item \Description Should a local scale be estimated? Not allowed with \kw{scale-file}, but can be used both with given and estimated wavelet.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{wavelet-3d}}\newkw{wavelet-3d}
 \slist
   \item \Description Information about the 3D-wavelet for this angle and seismic type. If not given, a 1D-wavelet is assumed.
   \item \Argument Elements containing information about the 3D-wavelet
   \item \Default
 \elist

\paragraph{\hbracket{file-name}}\rnewkw{file-name}{file-name3}
 \slist
   \item \Description File name for the 1D-wavelet file. This 1D-wavelet will define the 3D-wavelet in combination with the filter given in \kw{filter-file-name}. If not given, the 1D-wavelet is estimated.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{filter-file-name}}\newkw{filter-file-name}
 \slist
   \item \Description File name for 3D-wavelet damping factor filter file. The 3D-wavelet is defined by the 1D-wavelet and the filter. The 1D-wavelet is either given in \kw{file-name3} or estimated. In either case this filter file must be given.
   \item \Argument File name for the amplitude scalings in the wavenumber filter.
   \item \Default
 \elist

\paragraph{\hbracket{corrfactor-file-name}}\newkw{corrfactor-file-name}
 \slist
   \item \Description File name for 3D-wavelet correction filter filter file. This is used to set up the noise model for the 3D-wavelet.
   \item \Argument File name for the correction factors in the wavenumber filter.
   \item \Default
 \elist

\paragraph{\hbracket{stretch-factor}}\newkw{stretch-factor}
 \slist
   \item \Description Stretch factor for 3D-wavelet. The pulse is stretch with this factor.
   \item \Argument Value > 0.0
   \item \Default 1.0
\elist

\paragraph{\hbracket{est-range-x}}\newkw{est-range-x}
 \slist
   \item \Description Range for area around the well in x-direction where data are used in 3D wavelet estimation. 
   \item \Argument Value >= 0.0
   \item \Default 0.0
\elist

\paragraph{\hbracket{est-range-y}}\newkw{est-range-y}
 \slist
   \item \Description Range for area around the well in y-direction where data are used in 3D wavelet estimation. 
   \item \Argument Value >= 0.0
   \item \Default 0.0
\elist

\subsubsection{\hbracket{match-energies}}\newkw{match-energies}
 \slist
   \item \Description If 'yes', signal to noise ratio and wavelet scaling will be set to match model values with empirical values. Not a common estimator.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{signal-to-noise-ratio}}\newkw{signal-to-noise-ratio}
 \slist
   \item \Description Value for the signal to noise value. If not given, this will be estimated.
   \item \Argument Value
   \item \Default
 \elist

\subsubsection{\hbracket{local-noise-scaled}}\newkw{local-noise-scaled}
 \slist
   \item \Description Name of file with local noise.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{estimate-local-noise}}\newkw{estimate-local-noise}
 \slist
   \item \Description Can not say 'yes' here if \kw{local-noise-scaled} is given.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsection{\hbracket{wavelet-estimation-interval}}\newkw{wavelet-estimation-interval}
 \slist
   \item \Description Controls the time interval used for wavelet estimation by a top and base surface.
   \item \Argument Elements controlling the time interval used for wavelet estimation
   \item \Default By default, estimation is done from all available seismic and well data.
 \elist

\subsubsection{\hbracket{top-surface-file}}\newkw{top-surface-file}
 \slist
   \item \Description File name for storm surface file giving the top of the time interval used for wavelet estimation.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{base-surface-file}}\newkw{base-surface-file}
 \slist
   \item \Description File name for storm surface file giving the base of the time interval used for wavelet estimation.
   \item \Argument File name
   \item \Default
 \elist

\section{\hbracket{well-data}} \newkw{well-data}
 \slist
   \item \Description All information about the well data is collected here.
   \item \Argument Elements containing information about the well data
   \item \Default
 \elist

\subsection{\hbracket{log-names}} \newkw{log-names}
 \slist
   \item \Description CRAVA needs to find the time, vp, vs, density and possibly facies logs. The name of these logs in the well files are given here.
   \item \Argument Name of logs
   \item \Default
 \elist

\subsubsection{\hbracket{time}} \rnewkw{time}{time2}
 \slist
   \item \Description Name of the TWT log
   \item \Argument String
   \item \Default %'TWT'
 \elist

\subsubsection{\hbracket{vp}}\rnewkw{vp}{vp2}
 \slist
   \item \Description Name of the vp log. May not be given if \kw{dt} is given.
   \item \Argument String
   \item \Default
 \elist

\subsubsection{\hbracket{dt}}\newkw{dt}
 \slist
   \item \Description Name of the inverse vp log. May not be given if \rkw{vp}{vp2} is given.
   \item \Argument String
   \item \Default %'DT'
 \elist

\subsubsection{\hbracket{vs}}\rnewkw{vs}{vs2}
 \slist
   \item \Description Name of the vs log. May not be given if \kw{dts} is given.
   \item \Argument String
   \item \Default
 \elist

\subsubsection{\hbracket{dts}}\newkw{dts}
 \slist
   \item \Description Name of the inverse vs log. May not be given if \rkw{vs}{vs2} is given.
   \item \Argument String
   \item \Default %'DTS'
 \elist

\subsubsection{\hbracket{density}}\rnewkw{density}{density2}
 \slist
   \item \Description Name of the density log.
   \item \Argument String
   \item \Default %'RHOB'
 \elist

\subsubsection{\hbracket{facies}}\newkw{facies}
 \slist
   \item \Description Name of the facies log.
   \item \Argument String
   \item \Default %'FACIES'
 \elist

\subsection{\hbracket{well}}\newkw{well}
 \slist
   \item \Description Repeatable command, one for each well. Contains information about the wells.
   \item \Argument Elements containing information about the wells
   \item \Default
 \elist

\subsubsection{\hbracket{file-name}}\rrnewkw{file-name}{file-name2}{file-name3}
 \slist
   \item \Description File name for a well file. RMS or Norsar format.
   \item \Argument File name
   \item \Default
 \elist


\subsubsection{\hbracket{use-for-wavelet-estimation}}\newkw{use-for-wavelet-estimation}
 \slist
   \item \Description Should this well be used for wavelet estimation?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{use-for-background-trend}}\newkw{use-for-background-trend}
 \slist
   \item \Description Should this well be used for background trend estimation?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{use-for-facies-probabilities}}\newkw{use-for-facies-probabilities}
 \slist
   \item \Description Should this well be used for facies probability estimation?
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{synthetic-vs-log}}\newkw{synthetic-vs-log}
 \slist
   \item \Description Is the Vs log in this well synthetic? Will be detected from Vp correlation if not specified here.
   \item \Argument 'yes' or 'no'
   \item \Default
 \elist

\subsubsection{\hbracket{optimize-location-to}}\newkw{optimize-location-to}
 \slist
   \item \Description Repeatable command, one for each offset angle used for estimating optimized well location for this well.
   \item \Argument Elements controlling optimization of well location
   \item \Default
 \elist

\paragraph{\hbracket{angle}}\rrnewkw{angle}{angle2}{angle3}
 \slist
    \item \Description Offset angle used for estimating optimized well location
    \item \Argument Value
    \item \Default
 \elist

\paragraph{\hbracket{weight}}\newkw{weight}
 \slist
    \item \Description Weight of the offset angle given in \rrkw{angle}{angle2}{angle3}
    \item \Argument Value
    \item \Default 1
 \elist

\subsection{\hbracket{high-cut-seismic-resolution}}\newkw{high-cut-seismic-resolution}
 \slist
   \item \Description This frequency is used to filter wells down to seismic resolution. Only used to generate output logs for QC.
   \item \Argument Value
   \item \Default
 \elist

\subsection{\hbracket{allowed-parameter-values}}\newkw{allowed-parameter-values}
 \slist
   \item \Description Sometimes there are faulty values in well logs. Here, trigger values for error detection can be controlled. These fall in two categories: Actual log values that are wrong, or logs that have extremely low or high variance when the background model is subtracted.
   \item \Argument Elements controlling trigger values for error detection
   \item \Default
 \elist

\subsubsection{\hbracket{minimum-vp}}\newkw{minimum-vp}
 \slist
   \item \Description Value for the smallest legal vp value.
   \item \Argument Value
   \item \Default 1300 m/s
 \elist

\subsubsection{\hbracket{maximum-vp}}\newkw{maximum-vp}
 \slist
   \item \Description Value for the largest legal vp value.
   \item \Argument Value
   \item \Default 7000 m/s
 \elist

\subsubsection{\hbracket{minimum-vs}}\newkw{minimum-vs}
 \slist
   \item \Description Value for the smallest legal vs value.
   \item \Argument Value
   \item \Default 200 m/s
 \elist

\subsubsection{\hbracket{maximum-vs}}\rnewkw{maximum-vs}{maximum-vs2}
 \slist
   \item \Description Value for the largest legal vs value.
   \item \Argument Value
   \item \Default 4200 m/s
 \elist

\subsubsection{\hbracket{minimum-density}}\newkw{minimum-density}
 \slist
   \item \Description Value for the smallest legal density value.
   \item \Argument Value
   \item \Default 1.4 g/cm$^3$
\elist

\subsubsection{\hbracket{maximum-density}}\newkw{maximum-density}
 \slist
   \item \Description Value for the largest legal density value.
   \item \Argument Value
   \item \Default 3.3 g/cm$^3$
 \elist

\subsubsection{\hbracket{minimum-variance-vp}}\newkw{minimum-variance-vp}
 \slist
   \item \Description Value for the smallest legal variance in the vp log after the background is subtracted and logarithm is taken.
   \item \Argument Value
   \item \Default 0.0005
 \elist

\subsubsection{\hbracket{maximum-variance-vp}}\newkw{maximum-variance-vp}
 \slist
   \item \Description Value for the largest legal variance in the vp log after the background is subtracted and logarithm is taken.
   \item \Argument Value
   \item \Default 0.0250
 \elist

\subsubsection{\hbracket{minimum-variance-vs}}\newkw{minimum-variance-vs}
 \slist
   \item \Description Value for the smallest legal variance in the vs log after the background is subtracted and logarithm is taken.
   \item \Argument Value
   \item \Default 0.0010
 \elist

\subsubsection{\hbracket{maximum-variance-vs}}\newkw{maximum-variance-vs}
 \slist
   \item \Description Value for the largest legal variance in the vs log after the background is subtracted and logarithm is taken.
   \item \Argument Value
   \item \Default 0.0500
 \elist

\subsubsection{\hbracket{minimum-variance-density}}\newkw{minimum-variance-density}
 \slist
   \item \Description Value for the smallest legal variance in the density log after the background is subtracted and logarithm is taken.
   \item \Argument Value
   \item \Default 0.0002
 \elist

\subsubsection{\hbracket{maximum-variance-density}}\newkw{maximum-variance-density}
 \slist
   \item \Description Value for the largest legal variance in the density log after the background is subtracted and logarithm is taken.
   \item \Argument Value
   \item \Default 0.0100
 \elist

\subsection{\hbracket{maximum-deviation-angle}}\newkw{maximum-deviation-angle}
 \slist
   \item \Description Value for the maximum deviation angle of a well before it is excluded from estimation based on vertical wells (such as wavelet and signal to noise).
   \item \Argument Value
   \item \Default 15
 \elist

\subsection{\hbracket{maximum-rank-correlation}}\newkw{maximum-rank-correlation}
 \slist
   \item \Description If the correlation between vp and vs logs exceed this value, the vs log is considered to be synthetic, and not counted as additional data in estimation.
   \item \Argument Value close to, but less than 1.
   \item \Default 0.99
 \elist

\subsection{\hbracket{maximum-merge-distance}}\newkw{maximum-merge-distance}
 \slist
   \item \Description Value giving the minimum distance in time between well log entries before they are merged to one observation.
   \item \Argument Value
   \item \Default 0.01
 \elist

\subsection{\hbracket{maximum-offset}}\newkw{maximum-offset}
 \slist
   \item \Description Value giving the maximum allowed offset for moving wells.
   \item \Argument Integer value
   \item \Default 5
 \elist

\subsection{\hbracket{maximum-shift}}\newkw{maximum-shift}
 \slist
   \item \Description Value giving the maximum allowed vertical shift for moving wells.
   \item \Argument Value
   \item \Default 11.0
 \elist

\section{\hbracket{prior-model}}\newkw{prior-model}
 \slist
   \item \Description This command defines the prior model for elastic parameters and possibly also facies.
   \item \Argument Elements defining prior models for elastic parameters and facies
   \item \Default
 \elist

\subsection{\hbracket{background}}\rrnewkw{background}{background2}{background3}
 \slist
   \item \Description Contains information about the background model or how to estimate it. Note that either all parameters must be given, or all must be estimated.
   \item \Argument Elements containing information about the background model
   \item \Default
 \elist

\subsubsection{\hbracket{vp-file}}\newkw{vp-file}
 \slist
   \item \Description File name for storm, segy, or crava grid file, giving background vp. Can not be given together with \kw{vp-constant}.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{vs-file}}\newkw{vs-file}
 \slist
   \item \Description File name for storm, segy, or crava grid file, giving background vs. Can not be given together with \kw{vs-constant}.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{density-file}}\newkw{density-file}
 \slist
   \item \Description File name for storm, segy, or crava grid file,giving background density. Can not be given together with \kw{density-constant}.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{vp-constant}}\newkw{vp-constant}
 \slist
   \item \Description Value, used for constant vp background. Can not be given together with \kw{vp-file}.
   \item \Argument Value
   \item \Default
 \elist

\subsubsection{\hbracket{vs-constant}}\newkw{vs-constant}
 \slist
   \item \Description Value, used for constant vs background. Can not be given together with \kw{vs-file}.
   \item \Argument Value
   \item \Default
 \elist

\subsubsection{\hbracket{density-constant}}\newkw{density-constant}
 \slist
   \item \Description Value, used for constant density background. Can not be given together with \kw{density-file}.
   \item \Argument Value
   \item \Default
 \elist

\subsubsection{\hbracket{velocity-field}}\rnewkw{velocity-field}{velocity-field2}
 \slist
   \item \Description File name for storm grid bile giving a velocity field used as base for vp in background estimation. Can not be used if the background parameters are given.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{lateral-correlation}}\newkw{lateral-correlation}
 \slist
   \item \Description 2D variogram for the lateral correlation in the elastic parameters in the estimated background model, used for kriging of wells. Can not be used if the background parameters are given.
   \item \Argument 2D variogram
   \item \Default
 \elist

\subsubsection{\hbracket{high-cut-background-modelling}}\newkw{high-cut-background-modelling}
 \slist
   \item \Description Value giving the maximum frequency in the estimated background model. Can not be used if the background parameters are given.
   \item \Argument Value
   \item \Default
 \elist

\subsection{\hbracket{lateral-correlation}}\rnewkw{lateral-correlation}{lateral-correlation2}
 \slist
   \item \Description 2D variogram for the lateral correlation in the elastic parameters.
   \item \Argument 2D variogram
   \item \Default
 \elist

\subsection{\hbracket{temporal-correlation}}\newkw{temporal-correlation}
 \slist
   \item \Description File name for the temporal correlation file.
   \item \Argument File name
   \item \Default
 \elist

\subsection{\hbracket{parameter-correlation}}\newkw{parameter-correlation}
 \slist
   \item \Description File name for the parameter correlation file.
   \item \Argument File name
   \item \Default
 \elist

\subsection{\hbracket{correlation-direction}}\newkw{correlation-direction}
 \slist
   \item \Description File name for the storm surface file giving the correlation direction for the inversion.
   \item \Argument File name
   \item \Default
 \elist

\subsection{\hbracket{facies-probabilities}}\rnewkw{facies-probabilities}{facies-probabilities2}
 \slist
   \item \Description Commands controlling the generating of facies probabilities.
   \item \Argument Elements controlling facies probabilities
   \item \Default
 \elist

\subsubsection{\hbracket{use-vs-for-facies-probabilities}}\newkw{use-vs-for-facies-probabilities}
\slist
  \item \Description Decides whether \vs is used when computing facies probabilities.
  \item \Argument'yes' or 'no'.
  \item \Default 'yes'.
\elist

\subsubsection{\hbracket{facies-estimation-interval}}\newkw{facies-estimation-interval}
 \slist
   \item \Description Defines an interval for estimation of facies probability given elastic parameters.
   \item \Argument Elements defining estimation interval
   \item \Default Everywhere facies and elastic logs are present.
 \elist

\paragraph{\hbracket{top-file-name}}\newkw{top-file-name}
 \slist
   \item \Description File name for storm surface file giving the top of the estimation interval.
   \item \Argument File name
   \item \Default
 \elist

\paragraph{\hbracket{base-file-name}}\newkw{base-file-name}
 \slist
   \item \Description File name for storm surface file giving the base of the estimation interval.
   \item \Argument File name
   \item \Default
 \elist

\subsubsection{\hbracket{prior-facies-probabilities}}\newkw{prior-facies-probabilities}
 \slist
   \item \Description Prior facies probabilities are given for all facies. Priors can be given as constant numbers or storm cubes. If this command is not given, prior distribution is estimated from wells.
   \item \Argument Elements controlling facies probabilities
   \item \Default
 \elist

\paragraph{\hbracket{facies}}\rnewkw{facies}{facies2}
 \slist
   \item \Description Repeatable command, one for each facies. All facies present in well logs must be given.
   \item \Argument Elements containing information about the facies
   \item \Default
 \elist

\subparagraph{\hbracket{name}}\newkw{name}
 \slist
   \item \Description Name of facies.
   \item \Argument Facies name
   \item \Default
 \elist

\subparagraph{\hbracket{probability}}\newkw{probability}
 \slist
   \item \Description Probability for the facies given above. Either this command or \kw{probability-cube} is given, same for all facies.
   \item \Argument Real numbers between 0 and 1. Numbers for all facies must sum to one.
   \item \Default
 \elist

\subparagraph{\hbracket{probabilitycube}}\newkw{probability-cube}
 \slist
   \item \Description File name for file containing prior facies probability for facies with name given above. Either this command or \kw{probability} is given, same for all facies.
   \item \Argument File name
   \item \Default
 \elist


\subsubsection{\hbracket{facies-probability-undefined-value}}\newkw{facies-probability-undefined-value}
 \slist
   \item \Description Value defining how large the undefined probability will be when facies probabilities are computed. This value is scaled and used as likelihood for undefined when facies probabilities are computed.
   \item \Argument Value
   \item \Default 0.01
 \elist

\section{\hbracket{variogram-keyword}}\newkw{variogram-keyword}
 \slist
   \item \Description Variograms are given on the following form
   \item \Argument
   \item \Default
 \elist

\subsection{\hbracket{variogram-type}}\newkw{variogram-type}
 \slist
   \item \Description Either 'genexp' or 'spherical' for general exponential or spherical variogram.
   \item \Argument
   \item \Default
 \elist

\subsection{\hbracket{angle}}\rnewkw{angle}{angle2}
 \slist
   \item \Description Value for the azimuth direction.
   \item \Argument
   \item \Default
 \elist

\subsection{\hbracket{range}}\newkw{range}
 \slist
   \item \Description Value for the range in the azimuth direction.
   \item \Argument
   \item \Default
 \elist

\subsection{\hbracket{subrange}}\newkw{subrange}
 \slist
   \item \Description Value for the range normal to the azimuth direction.
   \item \Argument
   \item \Default
 \elist

\subsection{\hbracket{power}}\newkw{power}
 \slist
   \item \Description Value between 1 and 2 for the power of the general exponential variogram. Not allowed for spherical variogram.
   \item \Argument
   \item \Default
 \elist

All angles are given as mathematical angles in degrees.
